---
title: "Exercise 1 (part b)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


3. Create an HTML document that samples 100 values from a log-normal
distribution (say, mu=1, sigma=.25); create a histogram of the distribution and
the distribution on the log scale; report the mean and variance of the sample in
line in the text. In general, do not just dump the R code and plots in the HTML
document; break your exercises into sections with headings, add some text
and make it readable.


**Solution**

```{r, echo = TRUE, include = TRUE} 

# specify values
n <- 100
mu <- 1
sigma <- 0.25

# sample from log normal
lnorm <- rlnorm(n, meanlog = mu, sdlog = sigma)

# Histogram of the distribution
par(mfrow = c(1,2))
hist(lnorm, main = "Lognormal distribution", col = "lightgreen")
hist(log(lnorm), main = "Log(lognormal distribution)", col = "lightblue")

```


The figure summarizes two histograms, one of the lognormal distribution (with mean $\mu=$ `r mu` and standard deviation $\sigma=$ `r sd`) and one of the lognormal distribution on the log scale (with mean $\mu=$ `r log(mu)` and standard deviation $\sigma=$ `r log(sd)`).